---
title: "Reproducible Report"
author: "Chase Clark"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, echo=FALSE}
# Load packages
library(ggplot2)
```
Preferably use :: to specify namespace, rather than calling library(). This is will make it easier for others to understand what functions come from which package (and easier for you in 6-months). For some packages I still use library() because it's much eassier (eg ggplot2)

More info on the data here:
https://www.glerl.noaa.gov/metdata/chi/metadata.html

Retrieve results using tested functions
```{r}
# Get url:
yesterday_url <- autoReportR::urlGenerator()
yesterday_data <- autoReportR::readNoaa(yesterday_url)
```

Quick peek:
```{r echo=FALSE}
head(yesterday_data)
```

Simple plot
```{r echo=FALSE}
ggplot(yesterday_data,
       aes(x = `C`,
           y = `X.`)) + 
    geom_point() + 
    geom_smooth() +
  xlab("AirTemp ") + 
  ylab("Relative Humidity")
```

Looks weird huh?

Can you guess why? (hint: probably only wrong in winter)
